---
title: "PackageTest"
author: "Nicole Grunert"  # or: author: (new line) - Nicole Grunert (new line) - other Author
date: '`r Sys.Date()`'
bibliography: my_references.bib
#output: html_document  # .yml or meta chunk html_documentbookdown::word_document2
output: bookdown::word_document2
---
# challenges: 
# create analysis directory
# create rmd in that directory
# use bookdown to get cap/cross-refs
# write a fn in R
# document your function with roxygen
# use the function in your rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# rubish

just learning learning learning

```{r}
library(mytestpkg)
```

# function

rubish function that doesnt work properly

```{r}
plot(-1, xlim = c(0,5), ylim = c(0,5))
curve(5*x^3,add=T)    # Plot an equation as a curve
```

# bibliographic citations example

<!--
see above: bibliography: my_references.bib  (need BibTex citations!)
-->
 reproducible research is important [@hillier1976space]
 
 more than one author:[see these ones: @hillier1976space;@jammer1969concepts;@gregory1994geographical]
 
 @gregory1994geographical is a very good paper...
 
 Hillier build the whole concept of Space Syntax Theory [-@hillier1976space]

here is a footnote: ^[Text and things]


# License

> devtools::use_mit_license()
* Updating license field in DESCRIPTION.
* Creating `LICENSE` from template.
> devtools::use_testthat()
* Adding testthat to Suggests
* Creating `tests/testthat`.
* Creating `tests/testthat.R` from template.



