---
title: "HarranPlain"
author: "Nicole Grunert"
date: "20 Juli 2017"
bibliography: my_references.bib
#output: html_document  # .yml or meta chunk html_document bookdown::word_document2
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Point Pattern

```{r}
harran=read.table("../data/Sites_HarranPlain.csv",
           sep = ",",
           header = TRUE)   # when knitting: "../data/Sites_HarranPlain.csv"!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
str(harran)
```

## spatstat

```{r}
library(sp)
coordinates(harran) <- ~X+Y
proj4string(harran) <- CRS("+init=epsg:4326")

harran <- spTransform(harran, CRSobj = CRS("+init=epsg:32637"))
str(harran) # for checking


library(spatstat)

str(harran@coords) # structure

harran_ppp <- ppp(x=harran@coords[,1],
                  y=harran@coords[,2],
                  window = owin(xrange = harran@bbox[1,],
                                yrange = c(min(harran@coords[,2]),
                                           min(harran@coords[,2])+52000)))


harran_ppp=unique.ppp(harran_ppp) # shows number of duplicated points and deletes them/ harran_ppp= has to be done to define harran_ppp new

str(harran_ppp)
plot(harran_ppp)

library(mapview)
mapview(harran)

```

## Challenge: delete duplicated points


```{r ch1}
harran_ppp=unique.ppp(harran_ppp) # shows number of duplicated points and deletes them/ harran_ppp= has to be done to define harran_ppp new


# or:
#anyDuplicated(harran_ppp)
#harran <- unique(harran_ppp)
#harran_ppp <- harran_ppp[!duplicated(harran_ppp)]

plot(harran_ppp)

```

#Nearest neighbour distance

```{r ch2}

harran_ppp_nn <- nndist(harran_ppp)
str(harran_ppp_nn) # shows distance within the structure(str)

hist(harran_ppp_nn)  # plots the nearest neighbour
#barplot(sort(harran_ppp_nn))

```

# challenge: create a kernel density estimation

```{r ch3}

harran_kde <- density.ppp(harran_ppp, sigma = mean(harran_ppp_nn))# see: likelihood cross validation bandwidth selection for kernel density (help)
plot(harran_kde)

```

# raster

```{r ch4}

library(raster)
dem <- raster("../data/dem.tif") # see above for problems when knitting

# or: library(rgdal)
#dem <- readGDAL("data/dem.tif")
plot(dem)

im_dem <- as.im(as.image.SpatialGridDataFrame(as(dem, "SpatialGridDataFrame"))) #creates image
plot(im_dem)


```


# challenge: use rhohat and create a plot

```{r ch5}

#?rhohat # smoothing estimate: changes the raster
harran_rhohat <- rhohat(harran_ppp, im_dem, bw = 200)
              # <- rhohat(harran_ppp, im_dem, bw=200) /gives a more distinct picture

plot(harran_rhohat) #x=elevation y=relative intensity of points -> relation of elevation to pointdensity, bandwidth=default -> default=sigma in the structure of the object(str(harran_rhohat))

rho_dem <- predict(harran_rhohat)
plot(rho_dem)

diff_rho <- harran_kde-rho_dem
plot(diff_rho)

```

# challenge: test poisson, create random points with rpoispp function that have the same intensity like our points

```{r ch6}

set.seed(123)
harran_rpoispp2 <- rpoispp(lambda = harran_ppp$n/area.owin(harran_ppp$window), win=harran_ppp$window)
set.seed(123)
harran_rpoispp3 <- rpoispp(intensity(harran_ppp), win=Window(harran_ppp))
set.seed(123)
harran_rpoispp4 <- rpoispp(ex = harran_ppp)

plot(harran_ppp)
points(harran_rpoispp2, col="green")
points(harran_rpoispp3, col="blue")
points(harran_rpoispp4, col="red")

# first block is all the same, different ways to get the same result
```

#Second order effects

```{r ch7}

harran_g <- Gest(harran_ppp)
str(harran_g)
plot(harran_g) # x=closest neighbours expected (blue), the rest shows higher than expected clusters y= distance

harran_ge <- envelope(harran_ppp, fun = "Gest") # calculates g function for random points
plot(harran_ge) # grey shadow_ monte Carlo Simulation

```

<!--
str(harran_g) ->
Classes ‘fv’ and 'data.frame':	513 obs. of  7 variables:
 $ r      : num  0 13.3 26.7 40 53.4 ... # distance measure
 $ theo   : num  0.00 4.39e-05 1.76e-04 3.95e-04 7.02e-04 ...
 $ han    : num  0 0 0 0 0 ...
 $ rs     : num  0 0 0 0 0 ...
 $ km     : num  0 0 0 0 0 ...
 $ hazard : num  0 0 0 0 0 ...
 $ theohaz: num  0.00 6.58e-06 1.32e-05 1.97e-05 2.63e-05 ...
 - attr(*, "argu")= chr "r"
 - attr(*, "valu")= chr "km"
 - attr(*, "ylab")= language G(r)
 - attr(*, "yexp")= language G(r)
 - attr(*, "fmla")= chr ".~r"
 - attr(*, "alim")= num  0 2628
 - attr(*, "labl")= chr  "r" "%s[pois](r)" "hat(%s)[han](r)" "hat(%s)[bord](r)" ...
 - attr(*, "desc")= chr  "distance argument r" "theoretical Poisson %s" "Hanisch estimate of %s" "border corrected estimate of %s" ...
 - attr(*, "units")=List of 3
  ..$ singular  : chr "unit"
  ..$ plural    : chr "units"
  ..$ multiplier: num 1
  ..- attr(*, "class")= chr "units"
 - attr(*, "fname")= chr "G"
 - attr(*, "dotnames")= chr  "km" "rs" "han" "theo"
-->


# challenge: do F and K Function

```{r ch8}

#F-function:

harran_f <- Fest(harran_ppp)
plot(harran_f)

harran_fe <- envelope(harran_ppp, fun = "Fest") # calculates f function for random points
plot(harran_fe)

## red: expected, black deviates -> expect that the empty spaces are smaller than expected = clustered


#K-function

harran_k <- Kest(harran_ppp)
plot(harran_k)

harran_ke <- envelope(harran_ppp, fun = "Kest")
plot(harran_ke) 

```

# Inhomogeneous Poissonfunction G/F/K 


```{r ch9}

harran_gi <- Ginhom(harran_ppp, lambda = predict(harran_rhohat)) # harran_rhohat needs an bandwidth of 200
plot(harran_gi)


harran_fi <- Finhom(harran_ppp, lambda = predict(harran_rhohat))
plot(harran_fi)

#par(mfrow = c(1,2))
#plot(harran_gi, xlim = c(0,6000))
#plot(harran_g, xlim = c(0,6000))      Gegenüberstellung 

```



Note that the `echo = FALSE` parameter is added to the code chunk to prevent printing of the R code that generated the plot.
